---
title: "Male and Female Condom Availability"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, echo=FALSE}
library(tidyverse)
library(rvest)
library(httr)
```

```{r message=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r message=FALSE, echo=FALSE}
condom_data = 
  GET("https://data.cityofnewyork.us/resource/4kpn-sezh.csv") %>% 
  content("parsed")
cleaned_data = 
  condom_data %>% 
  select(facility_pk, facilityname, partnertype, partner_type_detailed, 
         address, borough, zipcode, latitude, longitude, phone, condoms_male,
         fc2_female_insertive_condoms, lubricant) %>% 
  rename(condoms_female = fc2_female_insertive_condoms) %>% 
  rename(partner_subtype = partner_type_detailed) %>% 
  mutate(
    condoms_male = as.factor(condoms_male), 
    condoms_male = fct_recode(condoms_male, "0" = "FALSE", "1" = "TRUE"),
    condoms_female = as.factor(condoms_female),
    condoms_female = fct_recode(condoms_female, "0" = "FALSE", "1" = "TRUE"),
    lubricant = as.factor(lubricant),
    lubricant = fct_recode(lubricant, "0" = "FALSE", "1" = "TRUE"),
    borough = as.factor(borough)
  )

cleaned_data$partnertype[cleaned_data$partnertype == "Community Based Organization/Non-Profit"] =
  "Community-Based Organization/Non-Profit"

```

## Distribution of Female and Male Condoms by Venue

Below is a barplot showing the distribution of female and male condoms by venue.

```{r message=FALSE}
tidy_data_partnertype =
  cleaned_data %>% 
  pivot_longer(
    condoms_male:condoms_female,
    names_to = "type_of_condom",
    values_to = "availability") %>%
  filter(availability == 1) %>% 
  group_by(partnertype, type_of_condom) %>% 
  summarize(n_obs = n()) %>% 
  ggplot(aes(x = partnertype, y = n_obs,
             fill = type_of_condom)) +
  geom_bar(stat = "identity", 
                    position = position_dodge()) +
  labs(
    title = 
      "Count of Male and Female Condoms 
       by Partner Type",
    x = "Partner Type",
    y = "Count") +
  scale_fill_discrete(name = "Type of Condom", 
                      labels = c("Female Condom",
                                 "Male Condom")) +
  coord_flip()
tidy_data_partnertype
```

Based on the data, it seems that male condoms are more readily available compared to female condoms and this is observed in all venues. It is also shown that there are substantially more male condoms in businesses and community-based organizations compared to other organizations. This finding is the same for female condoms except that it is more common in community health centers than businesses.

```{r message=FALSE}
tidy_data_borough =
  cleaned_data %>% 
  pivot_longer(
    condoms_male:condoms_female,
    names_to = "type_of_condom",
    values_to = "availability") %>%
  filter(availability == 1) %>% 
  group_by(borough, type_of_condom) %>% 
  summarize(n_obs = n()) %>% 
    ggplot(aes(x = borough, y = n_obs,
             fill = type_of_condom)) +
  geom_bar(stat = "identity", 
                    position = position_dodge()) +
    labs(
    title = 
      "Count of Male and Female Condoms 
       by Borough",
    x = "Borough",
    y = "Count") +
  scale_fill_discrete(name = "Type of Condom", 
                      labels = c("Female Condom",
                                 "Male Condom")) +
  coord_flip()
tidy_data_borough 
```

There is not much variation between subtypes in the venues. Aside from the Other category, it seems like there are more male condoms in bars, barber shops, and clinical facilities. This also poses true for female condoms except they are not available as much in barber shops.

## Distribution of Female and Male Condoms by Venue Subtype

Below is a barplot showing the distribution of female and male condoms by venue subtype.

```{r message=FALSE}
tidy_data_partnersubtype =
  cleaned_data %>% 
  pivot_longer(
    condoms_male:condoms_female,
    names_to = "type_of_condom",
    values_to = "availability") %>%
  filter(availability == 1) %>% 
  group_by(partner_subtype, type_of_condom) %>% 
  summarize(n_obs = n()) %>% 
  ggplot(aes(x = partner_subtype, y = n_obs,
             fill = type_of_condom)) +
  geom_bar(stat = "identity", 
                    position = position_dodge()) +
  labs(
    title = 
      "Count of Male and Female Condoms 
       by Partner SubType",
    x = "Partner SubType",
    y = "Count") +
  scale_fill_discrete(name = "Type of Condom", 
                      labels = c("Female Condom",
                                 "Male Condom")) +
  coord_flip()
tidy_data_partnersubtype
```

