---
title: "Popular Venues"
output: html_document
---

```{r setup, message=FALSE, echo=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)
theme_set(theme_minimal())

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r message=FALSE, echo=FALSE}
condom_data = 
  GET("https://data.cityofnewyork.us/resource/4kpn-sezh.csv") %>% 
  content("parsed")

cleaned_data = 
  condom_data %>% 
  select(facility_pk, facilityname, partnertype, partner_type_detailed, address, borough, zipcode, latitude, longitude, phone, condoms_male, fc2_female_insertive_condoms, lubricant) %>% 
  rename(condoms_female = fc2_female_insertive_condoms) %>% 
  rename(partner_subtype = partner_type_detailed) %>% 
  mutate(
    condoms_male = as.factor(condoms_male), 
    condoms_male = fct_recode(condoms_male, "0" = "FALSE", "1" = "TRUE"),
    condoms_female = as.factor(condoms_female),
    condoms_female = fct_recode(condoms_female, "0" = "FALSE", "1" = "TRUE"),
    lubricant = as.factor(lubricant),
    lubricant = fct_recode(lubricant, "0" = "FALSE", "1" = "TRUE"),
    borough = as.factor(borough)
  )

cleaned_data$partnertype[cleaned_data$partnertype == "Community Based Organization/Non-Profit"] =
  "Community-Based Organization/Non-Profit"
```

## Overall Most Popular Venues

The table below shows the total number of distribution locations for each type of venue that distributes condoms. 

```{r}
pop_venue =
  cleaned_data %>% 
  group_by(partnertype) %>% 
  summarize(total_n = n()) %>% 
  arrange(desc(total_n))

pop_venue %>% 
  knitr::kable()
```

We can see that the most popular types of venues that distribute condoms are `r pop_venue$partnertype[1]` and `r pop_venue$partnertype[2]`. Surprisingly, Sexual Health Clinics only have `r pop_venue %>% filter(partnertype == "Sexual Health Clinics (NYC DOHMH)") %>% pull(total_n)` distribution locations.

```{r}
pop_venue %>% 
  head(5) %>% 
  mutate(partnertype = fct_reorder(partnertype, total_n, .desc = TRUE)) %>% 
  ggplot(aes(x = partnertype, y = total_n, fill = partnertype)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 8)) +
  labs(title = "Top 5 Most Popular Venue Types")
```

Visually, we can see that there are many more `r pop_venue$partnertype[1]` and `r pop_venue$partnertype[2]` venues that distribute condoms than any other venue type.

## Most Popular Venue Subtypes

The table below shows the total number of distribution locations for the top 10 most popular subtypes of venue that distribute condoms.

```{r}
pop_subtype =
  cleaned_data %>% 
  group_by(partner_subtype) %>% 
  summarize(total_n = n()) %>% 
  arrange(desc(total_n)) %>% 
  head(10)

pop_subtype %>% 
  knitr::kable()
```

We can see that the most popular subtype of venue that distributes condoms are not classified as anything specific; they are just categorized as `r pop_subtype$partner_subtype[1]`. The second most popular subtype of venue that distributes condoms is `r pop_subtype$partner_subtype[2]`.

To examine the next 9 most popular subtypes of venues that distribute condoms, we will look at a bar graph excluding the category Other.

```{r}
pop_subtype %>% 
  filter(partner_subtype != "Other") %>% 
  mutate(partner_subtype = fct_reorder(partner_subtype, total_n, .desc = TRUE)) %>% 
  ggplot(aes(x = partner_subtype, y = total_n, fill = partner_subtype)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
  labs(title = "Most Popular Venue Subtypes")
```

Visually, we can see that there are many more `r pop_subtype$partner_subtype[2]` venues that distribute condoms than any other subtype of venue.
