---
title: "Venues per Borough"
output: 
  html_document
---

```{r, message=FALSE}
library(tidyverse)
library(rvest)
library(httr)
```

```{r, message=FALSE}
condom_data = 
  GET("https://data.cityofnewyork.us/resource/4kpn-sezh.csv") %>% 
  content("parsed")

cleaned_data = 
  condom_data %>% 
  select(facility_pk, facilityname, partnertype, partner_type_detailed, 
         address, borough, zipcode, latitude, longitude, phone, condoms_male,
         fc2_female_insertive_condoms, lubricant) %>% 
  rename(condoms_female = fc2_female_insertive_condoms) %>% 
  rename(partner_subtype = partner_type_detailed) %>% 
  mutate(
    condoms_male = as.factor(condoms_male), 
    condoms_male = fct_recode(condoms_male, "0" = "FALSE", "1" = "TRUE"),
    condoms_female = as.factor(condoms_female),
    condoms_female = fct_recode(condoms_female, "0" = "FALSE", "1" = "TRUE"),
    lubricant = as.factor(lubricant),
    lubricant = fct_recode(lubricant, "0" = "FALSE", "1" = "TRUE"),
    borough = as.factor(borough)
  )

cleaned_data$partnertype[cleaned_data$partnertype == "Community Based Organization/Non-Profit"] =
  "Community-Based Organization/Non-Profit"
```  

### Number of venues per borough  
```{r, message=FALSE}
cleaned_data %>% 
  group_by(borough) %>% 
  summarize(n = n()) %>% 
  mutate(
    borough = fct_reorder(borough, n, .desc = TRUE)
  ) %>% 
  ggplot(aes(x = borough, y = n/sum(n), fill = borough)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(label = round(n/sum(n), 4)), vjust = -0.25) +
  labs(
    x = "Borough",
    y = "% of venues/facilities") + 
  ggtitle("Distribution of Venues/facilities Per Borough")
```

From the bar plot above, we can see that distribution of venues/facilities across the 5 boroughs. For example, over 2/3 of the total # of facilities are in Manhattan and Brooklyn alone, with Staten Island having the fewest number of facilities that offers free safer sex products (e.g., condoms, lubricants). This is not surprising, however, since Staten Island has a smaller population size. 

